Carbon Management Strategies for a Climate-Neutral European Economy

### 2024-01-01 report/submissions/journal/cover_letter/letter.tex
follow up

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		We are pleased to present our paper titled “\hydrogen{} and \carbon{} Network Strategies for the European Energy System.” This collaborative effort from researchers at the Institute of Energy Technology, Technical University of Berlin, contributes significantly to the critical discourse on climate-neutral energy systems in Europe.

		In our study, we introduce the first large-scale investment model to analyze potential synergies and competition between hydrogen and carbon dioxide transport networks within a carbon-neutral European energy system. Our model represents an advancement over existing models by optimizing a comprehensive range of technologies for the production, transportation, and storage of of hydrogen and carbon dioxide, along with other energy carriers, across all relevant sectors at high temporal and spatial resolution.

@@

		As underscored by our analysis, the integration of hydrogen and carbon dioxide networks into European energy policy is vital for a resilient, carbon-neutral, or negative future energy system.

>>>>

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		We are pleased to present our paper titled “\hydrogen{} and \carbon{} Network Strategies for the European Energy System.” This collaborative effort from researchers at the Institute of Energy Technology, Technical University of Berlin, contributes to the critical discourse on climate-neutral energy systems in Europe.

		In our study, we introduce the first large-scale investment model to analyze potential synergies and competition between hydrogen and carbon dioxide transport networks within a carbon-neutral European energy system. Our model represents an advancement over existing models by optimizing a comprehensive range of technologies for the production, transportation, and storage of hydrogen and carbon dioxide, along with other energy carriers, across all relevant sectors at high temporal and spatial resolution.

@@

		As underscored by our analysis, the integration of both hydrogen and carbon dioxide networks into European energy policy is vital for a resilient, carbon-neutral, or negative future energy system.
